An Algorithm for Constructing Monotone \\ Quintic Interpolating Splines

### 2019-12-16 Paper_[2019-11]_HPC/paper/paper.tex
Submitted the paper.

An algorithm for computing monotone order six piecewise polynomial
interpolants is proposed. Algebraic constraints for enforcing
monotonicity are provided that align with quintic monotonicity
theory. The algorithm is implemented, tested, and applied to several
sample problems to demonstrate the improved accuracy of monotone
quintic spline interpolants compared to that for monotone cubic spline
interpolants.

>>>>

An algorithm for computing monotone order six piecewise polynomial
interpolants is proposed. Algebraic constraints for enforcing
monotonicity are provided that align with quintic monotonicity
theory. The algorithm is implemented, tested, and applied to several
sample problems to demonstrate the improved accuracy of monotone
quintic spline interpolants compared to that for existing monotone cubic spline
interpolants.
